---
title: Group Accounting
author: ''
date: '2019-09-24'
slug: group-accounting
categories: []
tags: []
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center", fig.width = 4, fig.height = 3)

library(tidyverse)
library(ggdag)
```


**What do you purchase (Asset vs Business)?**


FRS 103(R) Business Combinations determines if an acquired set of activities and assets is a business;   

* A business includes an input and a substantive process that together significantly contribute to the **ability** to create output. e.g. special knowledge and skills, (unlike operating pools in real estate, shipping industry).
* Optional fair values concentration test: concentrated in a single or a group of similar identifiable asset.


Different accounting treatments accordingly;

* An asset: subject to impairment test.
* A business: is required to perform purchase price allocation during the consolidation process.


**Do you have control?**


FRS 110 determines the control concept;

* Power over the decision-making of relevant process and activities
* Returns
* Combination of power and returns (principal vs agent)


Powers -> Substantial rights -> Voting;

* Majority voting rights
* Contractual arrangements (among investors)
* Potential voting rights (options regardless of managment intention)
* De facto control (many minority investors)
* Purpose and designed SPV (expectation and motivation)
* Proof of the power of disposal (run BOD regardless of voting)


Substantial rights;

* Not protective
* Possibility of exercising (timing and feasibility)


**Am I exempted from consolidation?**


* Immaterial entities
* Subsidiaries recorded at FVTPL


**How to consolidate?**


Consolidation process;

* Convert local GAAP to IFRS in a single financial statements in terms of Recognition, Measurement, and Presentation.
* Align financial year end (a same reporting date or **within 3 months**)
* Currency translation (BS: close rate, PL: average rate, Equity: historical rate, translation reserve, OCI)
* Consolidation forms.
* Change consolidation levels (stepup acquisition or disposal)
* Intra-group transactions (IFRS: buyer tax rate, US: seller tax rate)


Consolidation forms;

* FRS 109: AFS at cost
* FRS 111 JO: Give parties **rights to specific** assets and obligations
* FRS 28(R) JV: Establish a seperate vehicle via the joint arrangement (no direct access to its assets)
* FRS 28(R) Associate: Significant influence, proportional consoldiation
* FRS 110 Subsidiries: Control, 100% consolidation
* FRS 105 Discontinued Operations: 


Purchase price (include both condideration and others, list others as follows);

* Transaction cost (DR: Expense, CR: Investment, not directly attributable to the acquisition)
* Contingent payments relating to post-acquisition
* Indemnification assets (due dilligence risk such as lawsuit, DR: Assets, CR: Provision)
* Pre-existing relationships (supplier contracts)
* Re-acquired rights (distribution rights)
* Leasing contracts
* Deferred tax


A faces a loss or penalty due to the **contract** with B. A intends to acquire B to imporve its financial position.

* Settlement is not done to obtain control over B upon acquisition (settlement recorded in P/L).
* Pre-existing relationships become an inter-company relationship, and is eliminated upon acquisition (must remove).
* Acquisition consideration = price - settlement (impact on goodwill)


A granted an exclusive **disribution right** to B (franchise). 

* The re-acquired right is treated as IA.
* Settlement in P/L: lower of unfavourable component (6/10 new right vs 6/10 old right) and termination penalty
* Difference (unfavourable component vs termination penalty) is treated as goodwill
* Acquisition consideration includes IA and goodwill.


```{r}
dagify(B ~ A,
       exposure = "A",
       outcome = "A") %>% 
  tidy_dagitty() %>% 
  ggdag() +
  theme_dag()
```


Purchase price allocation (Consideration);

* Cash
* Shares
* Previous interest
* NCI
* Fair value of assets (deferred tax)
* Contigent consideration (Earn-out (Yes): Future, Indemnification (No): Past)
* Goodwill


Earn-out contingent consideration;

* Cash settlement: libility at FV (must be included in group FS, FV based on probabilities, movement recoded in P/L)
* Sahre settlement: initially recorded at FV, subsequently equity without remeasurement.


Share-based payment;

* Share acquisition: A part of purchase consideration
* Share incentive: Post-acquisition expenses
* Replace the exisiting plan (Payment vs Vested, <= Consideration, > P/L as post-combination cost)


**How much to consolidate?**


Joint operation;

* % profit sharing in contracts
* line-by-line accounting based on %
* intra group transactions elimination


Joint venture;

* Equity accounting: Investment (dividend, profit), FV assets (depreciation, tax), contingent liabilities, goodwill (impariment).


Associates;

* Equity accounting


If B, C, D have a joint agreement, C has to prepares using equity accounting too.


```{r}
dagify(x ~ a30,
       x ~ b25,
       x ~ c15,
       x ~ d30,
       exposure = "x",
       outcome = "x") %>% 
  tidy_dagitty() %>% 
  ggdag() +
  theme_dag()
```


Subsidiries;

* Previously held interest is not remeasured **until** it becomes a subsidiary 
* AFS to Associate (Dr: Current investment, Cr: Previous equity, Cr: Cash)
* Associate to Subsidiary (DR: Investment, Cr: P/L, as if sell buy back, then consolidation allocation).
* Same treatment in the case of disposal.


If Co issues FG to the Bank, Co still has risks and rewards. Thus, Co has to consolidate SPV with 100% NCI. 


```{r}
dagify(SPV ~~ Co,
       SPV ~ Bank,
       Bank ~ Co,
       exposure = "SPV",
       outcome = "SPV") %>% 
  tidy_dagitty() %>% 
  ggdag() +
  theme_dag()
```


Loss of control after partial disposal;

* AFS reserve recycles to P/L (a part of disposal gain)
* Revaluation reserve recycles to R/E (not disposal gain)
* Accounting treatment should be same (recognize a full gain).


```{r}
dagify(X100 ~ A,
       Y ~ A,
       Y ~ B60,
       exposure = "Y",
       outcome = "X100") %>% 
  tidy_dagitty() %>% 
  ggdag() +
  theme_dag()
```


```{r}
dagify(Y ~ X100,
       Y ~ A,
       Y ~ B60,
       exposure = "Y",
       outcome = "X100") %>% 
  tidy_dagitty() %>% 
  ggdag() +
  theme_dag()
```



To read more, please refer to [2017 Under control Applying IFRS 10](https://www.grantthornton.global/en/insights/articles/under-control-applying-ifrs-10/)






