---
title: Audit Data Analytics Part4
author: ''
date: '2019-11-18'
slug: audit-data-analytics-part4
categories: []
tags: []
---


```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE, comment = " ")

library(tidyverse)
library(rlang)
library(lubridate)

tb <- read_csv("C:/Users/Stewart Li/Dropbox/0. Stewart publication_Always updated/stdatascience/dsproject/auditworkpaper/data/gl.csv") %>% 
  rename(id = X1) %>% 
  select(-adj) %>% 
  filter(!is.na(type)) %>% 
  mutate(weekday = wday(date, label = TRUE),
         month = month(date, label = TRUE))

df_ar <- tb %>% 
  filter(subaccount %in% c("Accounts Receivable", "Revenue"))

pl <- unique(tb$subaccount)[19:62] %>% dput
df_pl <-tb %>% 
  filter(subaccount %in% pl, 
         !subaccount %in% c("Mileage", "Employee Bonus", "Sick/Holiday & Vacation Pay")) %>% 
  group_by(date, subaccount) %>% 
  summarise_at(vars(debit, credit), sum) %>% 
  mutate(amt = abs(credit - debit)) %>% 
  select(date, subaccount, amt) %>% 
  pivot_wider(names_from = subaccount, values_from = amt) %>% 
  replace(is.na(.), 0) %>% 
  select(date, Revenue, everything()) %>% 
  ungroup() %>% 
  janitor::clean_names()
```


This part covers EDA. Target variable is revenue. 


### Numeric descriptive statistics


```{r}
skimr::skim_to_wide(df_pl[-1])
```


### Target variables


**Central tendency**


```{r}
df_pl %>% 
  ggplot(aes(revenue)) +
  scale_x_log10(labels = scales::comma) +
  geom_histogram(aes(y = ..density..)) +
  geom_density(alpha = .2, fill = "firebrick") +
  theme_light() +
  labs(title = "Sales distribution",
       x = "Transformed Sales", 
       y = "Density")
```


**Normality**


p < .05 then the distribution in question is significantly different from a normal distribution.


```{r}
shapiro.test(df_pl$revenue)
```


```{r}
qqnorm(df_pl$revenue)
```


### Correlation


**Correlation matrix**


```{r}
corrplot::corrplot(cor(df_pl[-1]), type = "upper", 
                   method='color', 
                   tl.cex = .7, cl.cex = .7, 
                   number.cex = 0.7, order = "hclust")
```


**Selected variables**


Select those variables having at least 0.10 of correlation with the target variable.


```{r}
cor(df_pl[2:42]) %>% 
  as.data.frame() %>% 
  rownames_to_column() %>% 
  as_tibble() %>% 
  select(c(1:2, 5)) %>% 
  arrange(desc(abs(revenue))) %>% 
  slice(1:12)
```


```{r}
cor_numvar <- cor(df_pl[-1], use="pairwise.complete.obs")
cor_sorted <- as.matrix(sort(cor_numvar[,'revenue'], decreasing = TRUE))
corhigh <- names(which(apply(cor_sorted, 1, function(x) abs(x) > 0.1)))

cor_numvar <- cor_numvar[corhigh, corhigh]
cex.before <- par("cex")
par(cex = 0.6)
corrplot::corrplot.mixed(cor_numvar, tl.pos = "lt") # tl.col="black",
par(cex = cex.before)
```


**Partial correlation**


Purchase has the strongest relationship with sales.


```{r}
cor.test(df_pl$revenue, df_pl$purchases_cost_of_goods, use = 'complete.obs')
```


Holding other variables constant, purchase has the following relationship with sales.


```{r}
ppcor::pcor.test(x = df_pl$revenue, 
                 y = df_pl$purchases_cost_of_goods, 
                 z = df_pl[c(20:42)])
```


```{r}
df_pl %>% 
  ggplot(aes(revenue, purchases_cost_of_goods)) +
  geom_point() +
  geom_density_2d() +
  geom_smooth(method = "lm", se = FALSE, col = "red") +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(labels = scales::comma) +
  theme_light() +
  labs(y = "Purchases", 
       x = paste0("Sales", '\n', 'Correlation: ', 
              round(cor(df_pl$revenue, df_pl$purchases_cost_of_goods, use = 'complete.obs'), 2)))
```


### Categorical descriptive statistics


**Monthly sales distribution**


```{r}
"%||%" <- function(a, b) {
  if (!is.null(a)) a else b
}

geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                             position = "dodge", trim = TRUE, scale = "area",
                             show.legend = NA, inherit.aes = TRUE, ...) {
  layer(
    data = data,
    mapping = mapping,
    stat = stat,
    geom = GeomFlatViolin,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      trim = trim,
      scale = scale,
      ...
    )
  )
}

GeomFlatViolin <-
  ggproto("GeomFlatViolin", Geom,
          setup_data = function(data, params) {
            data$width <- data$width %||%
              params$width %||% (resolution(data$x, FALSE) * 0.9)
            
            # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
            data %>%
              group_by(group) %>%
              mutate(ymin = min(y),
                     ymax = max(y),
                     xmin = x,
                     xmax = x + width / 2)
            
          },
          
          draw_group = function(data, panel_scales, coord) {
            # Find the points for the line to go all the way around
            data <- transform(data, xminv = x,
                              xmaxv = x + violinwidth * (xmax - x))
            
            # Make sure it's sorted properly to draw the outline
            newdata <- rbind(plyr::arrange(transform(data, x = xminv), y),
                             plyr::arrange(transform(data, x = xmaxv), -y))
            
            # Close the polygon: set first and last point the same
            # Needed for coord_polar and such
            newdata <- rbind(newdata, newdata[1,])
            
            ggplot2:::ggname("geom_flat_violin", GeomPolygon$draw_panel(newdata, panel_scales, coord))
          },
          
          draw_key = draw_key_polygon,
          
          default_aes = aes(weight = 1, colour = "grey20", fill = "white", size = 0.5,
                            alpha = NA, linetype = "solid"),
          
          required_aes = c("x", "y")
  )


getPalette <- colorRampPalette(RColorBrewer::brewer.pal(8, "Set2"))(12) 
lb <- function(x) mean(x) - sd(x)
ub <- function(x) mean(x) + sd(x)

df_sum <- df_ar %>% 
  filter(subaccount == "Revenue") %>% 
  group_by(month) %>% 
  summarise_at(vars(credit), list(ymin = lb, ymax = ub, mean = mean))

df_ar %>% 
  filter(subaccount == "Revenue") %>% 
  ggplot(aes(factor(month), credit, fill = factor(month))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), trim = TRUE, alpha = .8, scale = "width") +
  geom_point(aes(y = credit, color = factor(month)), 
             position = position_jitter(width = .15), size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  geom_point(data = df_sum, aes(x = month, y = mean), 
             position = position_nudge(x = 0.3), size = 2.5) +
  geom_errorbar(data = df_sum, aes(ymin = ymin, ymax = ymax, y = mean), 
                position = position_nudge(x = 0.3), width = 0) +
  expand_limits(x = 5.25) +
  scale_y_continuous(labels = scales::comma) +
  scale_color_manual(values = getPalette) +
  scale_fill_manual(values = getPalette) +
  theme_light() +
  theme(legend.position="none") +
  labs(title = "Monthly sales distribution", 
       x = "", 
       y = "")
```


**Weekly sales distribution**


```{r}
df_ar %>% 
  filter(subaccount == "Revenue") %>% 
  mutate(weekday = fct_relevel(weekday, rev(c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")))) %>%
  ggplot(aes(weekday, credit)) +
  geom_boxplot() +
  geom_jitter(shape = 16, position = position_jitter(0.4), alpha = .3) +
  coord_flip() +
  scale_y_continuous(labels = scales::dollar) +
  stat_summary(fun.y = mean, geom = "point", shape = 13, size = 4, color = "firebrick") +
  theme_light() +
  labs(title = "Weekly sales distribution",
       x = "", 
       y = "")
```





