---
title: Audit Data Analytics Part3
author: ''
date: '2019-11-18'
slug: audit-data-analytics-part3
categories: []
tags: []
---


```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE, comment = " ")

library(tidyverse)
library(lubridate)
library(formattable)

tb <- read_csv("C:/Users/Stewart Li/Dropbox/0. Stewart publication_Always updated/stdatascience/dsproject/auditworkpaper/data/gl.csv") %>% 
  rename(id = X1) %>% 
  select(-adj) %>% 
  filter(!is.na(type)) %>% 
  mutate(weekday = wday(date, label = TRUE),
         month = month(date, label = TRUE))

df_ar <- tb %>% 
  filter(subaccount %in% c("Accounts Receivable", "Revenue"))
```


This part covers audit procedures generally performed on sales customers. 


**Sales summary table by customers and months**


```{r}
df_ar %>% 
  filter(subaccount == "Revenue") %>% 
  group_by(name, month) %>% 
  summarise(freq = n(),
            credit = sum(credit)) %>% 
  mutate(pct = credit / sum(credit),
         cum_amt = cumsum(credit),
         cum_pct = cumsum(pct)) %>% 
  head(10)
```


**Month over month sales by customers**


```{r}
mom_sales <- df_ar %>% 
  filter(subaccount == "Revenue") %>% 
  mutate(yearmonth = format(date, "%Y-%m")) %>% 
  group_by(yearmonth, name) %>% 
  summarise(monthlysales = sum(credit)) %>% 
  arrange(yearmonth, name) %>% 
  ungroup() %>% 
  group_by(name) %>% 
  mutate(mom = (monthlysales - lag(monthlysales)) / lag(monthlysales),
         mom = round(mom * 100, 1),
         yoy = (monthlysales - lag(monthlysales , 12)) / lag(monthlysales, 12),
         yoy = round(yoy * 100, 1))

mom_sales %>% 
  filter(!is.na(mom)) %>% 
  select(-yoy) %>%  
  arrange(desc(abs(mom)))
```


**Relative Size Factor test (RSF)** 


Could also include mean computed without the first larget number to help you decide relevant RSF score. Here, 0.6 is the chosen cut-off.


```{r}
df_ar %>% 
  filter(subaccount == "Revenue") %>% 
  group_by(name) %>% 
  arrange(desc(credit)) %>% 
  slice(1:2) %>% 
  mutate(rsf = credit / lag(credit)) %>% 
  filter(rsf >= 0.6) %>% 
  select(c(5:8, 15))
```


**Top 10 customers**


```{r}
df_ar %>%
  filter(subaccount == "Revenue") %>% 
  group_by(name = fct_lump(name, 10, w = credit)) %>% # top_n
  summarise(amt = sum(credit),
            freq = n()) %>%  
  arrange(desc(amt)) %>%  
  mutate(pct = round(amt / sum(amt), 2),
         pct = percent(pct, "d", digits = 0L),
         amt = currency(amt, "$", digits = 0L)) %>% 
  formattable(list(amt = color_bar("#FA614B"),
                   freq = color_bar("pink"),
                   pct = color_bar("lightpink")))
```


**Customer churn analysis (RFM)**


```{r}
df_ar %>% 
  filter(subaccount == "Revenue") %>% 
  select(date, name, credit) %>% 
  mutate(date = ceiling_date(date, "day")) %>% 
  group_by(name) %>% 
  mutate(revenue = sum(credit),
         last_visit = last(date),
         last_days =  as.double(as.Date("2018-12-31") - last_visit),
         orders = n()) %>% 
  select(-c(date, credit)) %>% 
  distinct(last_visit, .keep_all = TRUE) %>% 
  ggplot(aes(last_days, orders, size = revenue)) +
  geom_point() +
  geom_text(aes(label = paste0 (name, " | ", last_visit)), 
            hjust = 0, vjust = 1, 
            check_overlap = TRUE, size = 3, col = "steelblue") +
  scale_x_continuous(labels = function(x) paste0(x, "/days")) +
  scale_y_continuous(labels = function(x) paste0(x, "/orders")) +
  scale_size_continuous(name = "Revenue", labels = scales::comma_format()) +
  theme_minimal() +
  theme(legend.justification=c(1,1),
        legend.position = c(0.95, 0.95),
        legend.background = element_blank()) +
  labs(title = "RFM as at 2018/12/31", 
       caption = "RAudit Solution LLP | Stewart Li",
       x = "",
       y = "")
```


**Sales outliers**


```{r}
z <- df_ar %>% 
  filter(subaccount == "Revenue") %>% 
  mutate(z = ifelse(abs(scale(credit)) > 1.96, "z", "ok")) %>% 
  filter(z == "z")

df_ar %>% 
  filter(subaccount == "Revenue") %>% 
  ggplot() +
  geom_point(aes(credit, date, size = credit > 6000)) +
  geom_point(data = z, aes(credit, date, color = "red")) +
  geom_vline(xintercept = 3000, lty = 2, col = "red", size = 1) +
  geom_text(data = subset(df_ar %>% filter(subaccount == "Revenue"), credit > 3000),
            aes(credit, date, label = name), 
            vjust = 1,
            hjust = .1,
            check_overlap = TRUE, 
            col = "steelblue",
            size = 3) +
  scale_colour_manual(values = c("red"), guide = FALSE) +
  scale_size_manual(values = c(1, 3), guide = FALSE) +
  scale_x_continuous(labels = scales::comma_format()) +
  annotate("text", x = 3400, y = as.Date("2019-01-06"), label = "3,000", size = 3) +
  theme(legend.position = "none") +
  theme_minimal() + 
  labs(title = "Sales outliers for FY2018",
       subtitle = "Based on ML and Z score",
       caption = "RAudit Solution LLP | Stewart Li",
       x = "",
       y = "") 
```
















